Evaluating the Effects of Tracker Reliability and Field of View on a Target Following Task in Augmented Reality

### 2009-08-24 trunk/Paper/paper.tex
first page revisions

A task common to many AR X-ray systems is to follow, using the augmented overlay, a moving target that is occluded by objects in the real world.  Problems with the AR system tracking objects accurately is an issue which is likely to have an effect on task performance.  Since the augmented view is overlaid on top of the real view it is also interesting to study the effects of the varied size of augmented field of view as well as its interaction with tracking difficulties.  We created a task that aimed to study these effect in a generic fashion in order to be generalizable while still being grounded in reality.

In this study, we have implemented an AR simulation in virtual reality to examine the effects of varying FOV and sensor dropouts in a target following task.  An AR simulation gives us the ability to vary experiment conditions which may be difficult or even impossible to replicate on a real-world AR system.  It also gives us the ability to remove unnecessary factors from generating noise in our data, such as illumination or visibilty changes, weather problems, or environmental distractions.

We are considering FOV and the sensor dropouts, or persistence of the augmented imagery, as the varying components of immersion in our study.  This is based off of Slater's definition \cite{slater} of immersion as the ``objective level of fidelity of the sensory stimuli produced by a technological system,''  enabling us to view the components of immersion as controllable aspect of the technological system.

The AR simulation is built as a target following task, where the participant is placed inside a virtual room and visually follows a person outside, walking an unpredictable path.  We wish to answer the following questions.  What effect does varying the augmented FOV have on user task performance?  What effect do different dropout lengths have on performance?  What are the interactions between these two variables?

@@

Bane and H\"{o}llerer propose a set of AR tools for virtual X-ray vision \cite{1383060}.  Various augmented views are presented, each attempting to overcome the "Superman's X-ray vision" problem of presenting too much AR information to the user.  The toolset's usefulness is illustrated with an example of an outdoors user viewing the contents of a nearby building.

>>>>

A task common to many AR X-ray systems is to follow, using the augmented overlay, a moving target that is occluded by objects in the real world.  Accuracy in AR system object tracking is an issue which is likely to have an effect on task performance.  Since the augmented view is overlaid on top of the real view it is also interesting to study the effects of the varying sizes of augmented field of view as well as its interaction with tracking imperfections.  We created a task that aimed to study these effects in a generic fashion in order to be generalizable while still being grounded in reality.

In this study, we have implemented an AR simulation in virtual reality to examine the effects of varying FOV and sensor dropouts in a target following task.  We simulate video see-through AR using a VR head mounted display.  This AR simulation gives us the ability to vary experiment conditions which may be difficult or even impossible to replicate on a real-world AR system.  It also gives us the ability to remove unnecessary factors from generating noise in our data, such as illumination or visibility changes, weather problems, or environmental distractions.

We are considering FOV and the sensor dropouts, or persistence of the augmented imagery, as the varying components of immersion in our study.  We adhere to Slater's definition \cite{slater} of immersion as being the ``objective level of fidelity of the sensory stimuli produced by a technological system,''  enabling us to view the components of immersion as the directly controllable aspects of the technological system.

The AR simulation is built as a target following task.  The participant stands inside a virtual room and visually follows a person walking an unpredictable path outside the room.  We wish to answer the subsequent questions.  What effect does varying the augmented FOV have on user task performance?  What effect do different dropout lengths have on performance?  What are the interactions between these two variables?

@@

Bane and H\"{o}llerer propose a set of AR tools for virtual X-ray vision \cite{1383060}.  Various augmented views are presented, each attempting to overcome "Superman's X-ray vision" problem of presenting too much AR information to the user.  The toolset's usefulness is illustrated with an example of an outdoor user viewing the contents of a nearby building.
